Formalizing Stack Safety as a Security Property

### 2021-09-09 submission3/response.txt

We first address the most important high-level points, then go back to
fill in detailed responses to all points made in the reviews.

# Limitations #

Currently, discussion of our model's limitations is scattered
throughout the paper.  We will expand and organize it into an explicit
section, along the following lines:

@@

For example, we are currently working on extending the work to a model of a
Cheri-style hardware capability machine, Cerise, and have not encountered
major obstacles.

> How realistic is the RISCV specification? In other words, are there any
>  RISCV vulnerabilities that are not taken into account in your model?

We use the RISCV specification to demonstrate that our properties are
testable in a realistic setting. We do not aim to exercise the entire RISCV
specification, and the validity of the model is not dependent on the absence
of (not stack-related) vulnerabilities in the RISCV implementation. That said,
the RISCV specification we use is complete for user mode integer
instructions (RV32IM).

> More generally, what are the limitations of the presented work?

> For example, in the model, there seems to be no distinction between values and addresses; is it a limitation?

Conventional ISAs do not make this distinction.  Our ongoing work on the
Cerise capability machine formalization has required some
modifications to our model to distinguish values from addresses, as
they are _not_ the same in a capability machine, but it has little
global effect on the model itself. Indeed, distinguishing between
values and addresses is a higher-level abstraction that can "hide"
potential bugs resulting from implicit conversions between them, so we
feel it is preferable to model them as the same when possible.

@@

> Another example is the outside qualifier that characterizes only a whole
> component. Wouldn't you need a finer-grain access control policy (and a
> qualifier for partially outside components)?

We don't entirely understand this question, but we wonder whether there may
be some confusion arising from our use of the term "components."  In our
model (see line 398), components are already fine-grained: individual
registers and memory addresses. We recognize that this is a poor choice of
term given the common usage of component to refer to a larger module in a
compartmentalization context, and we plan to change the term to "state
elements."  Since components/elements are so fine-grained, there is no need
for finer access control.

> Could you comment on the Coq formalization that is provided as a
>  supplementary material? Was it straightforward to write a Coq program from
>  a C++ program? Moreover, I looked at the Coq development and found some
>  admitted lemmas in it.

The theorems and lemmas in the formalization files serve only as
sanity checks on our definitions. The Admitted and commented-out ones
are mostly part of an early effort to formalize the relationships
between our various properties, especially that Stepwise properties are stronger
than Observational. They were included by mistake.

### 2021-09-09 submission3/response.txt

- SubroutineSimple.v defines the basic stack safety properties.
  Some comments are outdated, and will be updated or removed for the final
  submission.

  \rightarrow_C => Line 126 (disregard comment regarding returns)
  Definition 5.2 => Line 184
  Definition 5.9 => Line 255
  Definition 5.10 => Line 277

- CalleeSave.v defines stack safety with callee-save registers.
  \rightarrow_C => Line 62
  Definition 8.6 => Line 123 & Line 130
  These definitions refer to general integrity and confidentiality properties for arbitrary
  traces defined in TraceProperties.v at Lines 51 & 60.

- SubroutineShare.v defines the version enhanced with argument passing on the stack.
  Note that a preliminary treatment of address-taken locals is present; we found this
  insufficient for inclusion in the paper.
  [APT: Does it differ from the (confusing) discussion at line 960?]

### 2021-09-09 submission3/response.txt

> I found the paper did not connect the section well. Section 4 presents a lot of details for a framework, which is then used in Section 5. Seem very disconnected? For instance, Line 501: ←C\leftarrow_C←C​ this has a different type to the semantics in the previous section. How does it relate? Generally, there are a lot of things that are similar to the previous section, but you are not actually connecting them. Is this because they are different or just missing exposition.

Much of the content that may seem disconnected takes the form of a
parameterizable relation and its various instantiations in different
versions of the property. \rightarrow_C is parameterized by the type ctx, which
is section 5 is instantiated as (K -> SD)x(list(target)). In later sections
it will be instantiated by other types.  Then for any \rightarrow_C, we can
extend \rightharpoonup to form \rightharpoonup_C.
[BCP: The formatting here makes it hard to read.  Can we improve it?]

We will do more to call out which parts of the formalization are
parameterized and when they are being instantiated, so that the connections
are clearer.

> Line 329: I was really interested in address taken at this point, and
>  whether the model could handle it. I really think the informal aspects of
>  the extensions, should be pulled forward, so these questions are answered
>  earlier

@@

This is a good point, and we will examine ways to introduce that
information sooner. But we are hesitant to go into too much detail on
variants while introducing the basic formalism, because it can be a
lot for the reader to keep track of.

> Line 349: How does this related to control flow integrity/guard, and
>  Intel's CET?

@@

> Line 508: "isRet" is a relation, but you are using as a function.

Yes, we will avoid this abuse of notation.

> Line 515: ReturnRec: This seems like it would allow you to access outer
  frames as long as you didn't return?

[LEO: Sean, check this.][SNA: I think they're confused about us allowing long returns.]
ReturnRec defines a return in the case that well-bracketedness does
not hold and a caller is returned to out of order. This has the cost of
additional complexity, but allows our integrity and confidentiality properties
to be orthogonal to well-bracketed control flow. It also opens the possibility
of implementing exceptions, as described in the Limitations section above.
So, accessing outer frames through ReturnRec is valid because if ReturnRec
applies, there has been a return.

### 2021-09-09 submission3/response.txt

[BCP: ???]  [APT: made a stab; others please check.]
The identification of call points, as described in this paragraph, is
required for all our properties: integrity, confidentiality, and
well-bracketed control flow (WBCF). Software or hardware support for
control flow integrity (e.g. the CET shadow stack) could be used to
enforce WBCF, but not the other two properties.

> Line 508: "isRet" is a relation, but you are using as a function.

Yes, we will avoid this abuse of notation.

> Line 515: ReturnRec: This seems like it would allow you to access outer
> frames as long as you didn't return?

ReturnRec allows us to handle the case that well-bracketedness is violated and
a caller is returned to before its callee. We choose to define this as a return,
so that integrity and confidentiality are meaningful even without 
well-bracketed control flow. This also opens the possibility
of implementing exceptions, as described in the Limitations section above.
In short, accessing outer frames through ReturnRec is valid because if ReturnRec
applies, there has been a return.

### 2021-09-09 submission3/response.txt

Core/ contains the abstract machine and policy models, as well as the RISCV
instantiations with different policies.

Properties/ contains Coq definitions corresponding to the different Properties:
- Trace.v and ObsTrace.v define the trace model and observation model

- SubroutineSimple.v defines the basic stack safety properties.
  Some comments are outdated, and will be updated or removed for the final
  submission.

  &#8594;<sub>C</sub> => Line 126 (disregard comment regarding returns)
  Definition 5.2 => Line 184
  Definition 5.9 => Line 255
  Definition 5.10 => Line 277

- CalleeSave.v defines stack safety with callee-save registers.
  &#8594;<sub>C</sub> => Line 62
  Definition 8.6 => Line 123 & Line 130
  These definitions refer to general integrity and confidentiality properties for arbitrary
  traces defined in TraceProperties.v at Lines 51 & 60.

@@

- SubroutineShare.v defines the version enhanced with argument passing on the stack.
  Note that a preliminary treatment of address-taken locals is present; we found this
  insufficient for inclusion in the paper.
  [APT: Does it differ from the (confusing) discussion at line 960?]

  &#8594;<sub>C</sub> => Line 82
  Definition 8.3 (Stepwise only) => Line 152
  Note that this definition refers to a general confidentiality property of traces defined in 
  TraceProperties.v at Line 35.

- Coroutine.v defines the coroutine version. Unlike in the paper, passing on the stack is included.
  &#8594;<sub>C</sub> => Line 107
  Definition 8.10 (Stepwise only) => Line 192 & Line 199
  Definition 8.11 (Stepwise only) => Line 212 & Line 221
  This also refers to the general properties presented in TraceProperties.v

@@

> The first example programs (Fig. 1 to 4) are C programs. The programs in Fig. 5 and 6 are qualified as C++ programs, but they could be C programs and they are close to the first programs. Moreover, the C syntax for passing parameters by reference is surprising. I would have written f(&x)(line 934) and void f(int *a)(line 944).

Only Fig. 6 uses C++ features.  Although C programmers might indeed
try to simulate call-by-reference by passing a pointer as suggested
here, this is subtly different from a genuine by-reference argument in
C++, because the latter cannot be directly used in a first-class way
in the callee (without using the & operator, as e.g. at line 945).
Thus, legal access to the value of a by-reference argument is
restricted to the immediate callee (and any chain of sub-callees to
which the argument is handed down by reference), and we can capture
this access pattern in our policies.  On the other hand, pointer
arguments might escape into arbitrary sub-callees, and there is no
obvious way for policies in our style to specify when access through
these pointers should be permitted. We will improve the discussion at
line 954ff to clarify this point.

___________________________________________________________________________
# Reviewer B

> I found the paper did not connect the section well. Section 4 presents a lot of details for a framework, which is then used in Section 5. Seem very disconnected? For instance, Line 501: ←C\leftarrow<sub>C</sub>←C​ this has a different type to the semantics in the previous section. How does it relate? Generally, there are a lot of things that are similar to the previous section, but you are not actually connecting them. Is this because they are different or just missing exposition.

Much of the content that may seem disconnected takes the form of a
parameterizable relation and its various instantiations in different
versions of the property. &#8594;<sub>C</sub> is parameterized by the type ctx, which
is section 5 is instantiated as (K -> SD)x(list(target)). In later sections
it will be instantiated by other types.  Then for any &#8594;<sub>C</sub>, we can
extend &#8640;  to form &#8640;<sub>C</sub>.

### 2021-09-09 submission3/response.txt

We thank the reviewers for their comments and questions.
We first address the most important high-level points, then go back to
fill in detailed responses to all points made in the reviews.

# Limitations #

Currently, discussion of our model's limitations is scattered
throughout the paper.  We will expand and organize it into an explicit
section, along the following lines:

Our focus is on characterizing stack safety.  So we are particularly
concerned with limitations that prevent the model from applying to
realistic uses of the stack, as opposed to modeling other structures
such as the heap, which we intentionally say nothing about.  (Heap
safety has already been studied, in isolation, by [Azevedo et al 2018],
and we expect that their correctness condition and ours can be
combined cleanly to characterize correct protection of stack + heap.)

@@

- Dynamic code generation. This would be rather challenging to
  integrate into our framework, because we rely on annotations in the
  code. We can easily envision supporting dynamic code generation
  where the generated code is guaranteed never to contain a call
  or other annotated instruction. We could also support annotated-code
  generation in which existing code is copied along with its annotations.

- Concurrency. We can handle a limited form of coroutines, as described in
  8.3. Handling full-blown preemptive concurrency would require significant
  changes in our underlying machine model.

# Supplementary Coq Material #

We should have referenced the supplementary material from the submission, and
described its purpose.

@@

- SubroutineSimple.v defines the basic stack safety properties.
  Some comments are outdated, and will be updated or removed for the final
  submission.

  \rightarrow_C => Line 126 (disregard comment regarding returns)
  Definition 5.2 => Line 184
  Definition 5.9 => Line 255
  Definition 5.10 => Line 277

- CalleeSave.v defines stack safety with callee-save registers.
  \rightarrow_C => Line 62
  Definition 8.6 => Line 123 & Line 130
  These definitions refer to general integrity and confidentiality properties for arbitrary
  traces defined in TraceProperties.v at Lines 51 & 60.

- SubroutineShare.v defines the version enhanced with argument passing on the stack.
  Note that a preliminary treatment of address-taken locals is present; we found this
  insufficient for inclusion in the paper.
_[APT: Does it differ from the (confusing) discussion at line 960?]_

@@

> Another example is the outside qualifier that characterizes only a whole
> component. Wouldn't you need a finer-grain access control policy (and a
> qualifier for partially outside components)?

We don't entirely understand this question, but we wonder whether there may
be some confusion arising from our use of the term "components."  In our
model (see line 398), components are already fine-grained: individual
registers and memory addresses. We recognize that this is a poor choice of
term given the common usage of component to refer to a larger module in a
compartmentalization context, and we plan to change the term to "state
elements."  Since components/elements are so fine-grained, there is no need
for finer access control.

> Could you comment on the Coq formalization that is provided as a
>  supplementary material? Was it straightforward to write a Coq program from
>  a C++ program? Moreover, I looked at the Coq development and found some
>  admitted lemmas in it.

_[APT: Include backward pointer re formalization.]_

The theorems and lemmas in the formalization files serve only as
sanity checks on our definitions. The Admitted and commented-out ones
are mostly part of an early effort to formalize the relationships
between our various properties, especially that Stepwise properties are stronger
than Observational ones. They were included by mistake.
_[APT: Maybe this should move up to the top-level discussion of the formalization? Not sure.]_

_[SNA: not sure what to say about writing Coq programs from C++ programs... really we wrote assembly programs anyway.]_
_[APT: here's a stab.]_
We don't quite understand this question; none of the Coq code was derived from C++.

@@

> Other comments

> The supplementary material is not mentioned in the submission. Links to the Coq formalization would have been useful (e.g., for definition 7.4 that I did not fully understand in the submission, as K' is defined but not used, and so is n'').

We agree, the Coq formalization should be better integrated into the submission, as described at the head of
this response. In the case of definition 7.4, this is a typo. The K in the third bullet should be K', and the
last instance of n' should be n''.

@@

> The first example programs (Fig. 1 to 4) are C programs. The programs in Fig. 5 and 6 are qualified as C++ programs, but they could be C programs and they are close to the first programs. Moreover, the C syntax for passing parameters by reference is surprising. I would have written f(&x)(line 934) and void f(int *a)(line 944).

Only Fig. 6 uses C++ features.  Although C programmers might indeed
try to simulate call-by-reference by passing a pointer as suggested
here, this is subtly different from a genuine by-reference argument in
C++, because the latter cannot be directly used in a first-class way
in the callee (without using the & operator, as e.g. at line 945).
Thus, legal access to the value of a by-reference argument is
restricted to the immediate callee (and any chain of sub-callees to
which the argument is handed down by reference), and we can capture
this access pattern in our policies.  On the other hand, pointer
arguments might escape into arbitrary sub-callees, and there is no
obvious way for policies in our style to specify when access through
these pointers should be permitted. We will improve the discussion at
line 954ff to clarify this point.

>    (310, 886,895,947) The return instruction is confusing as the return type of f is void.

[SNA: should we do jlr?]
[APT: The reviewer is uncomfortable seeing a C `return` with no argument. Not sure why.
I don't think this needs a response at all.]

> Questions for the response period

> See my former questions related to 1) the Coq formalization, 2) the choice of a RISCV model and 3) the limitations of the approach

@@

___________________________________________________________________________
# Reviewer B

> Paper summary

> This paper presents a semantics for formalising safety properties of stack safety enforcement systems. The paper uses a map to say which parts of the stack can currently be accessed and which can't, similar to the semantics of separation logic. It then connects this to a notion of call and return, that can be configured to enable different machine's implementations of functions.

> The paper uses a systematic testing approach with QuickChick to show that a hardware enforcement mechanism actually provides stack safety, and find bugs that are injected into the approach. It is great that you found the bug in lazy approach, however, it is fairly obvious type of security issue where uninitialised data leads to something escaping.

> The paper discusses extension, where parameter passing can use the stack, and passing references to structures.

> The paper is primarily a semantics paper, though that seems fairly straightforward. The more interesting aspect of the paper is the more elaborate examples in Section 6 and 7, and the more elaborate extensions in 8. But I had not followed the earlier aspects well enough to appreciate those.

> Overall, I didn't find the paper particularly compelling in its current form. It seems complex for what it achieves earlier on, and doesn't have clear enough exposition for the later parts.
> Strengths

>    Checks properties of stack safety using capabilities
>    Interesting topic

>    Exposition doesn't connect the different aspects of the paper well.

>    Seems overly complex in comparison to other relational reasoning papers.

@@

> I found the paper did not connect the section well. Section 4 presents a lot of details for a framework, which is then used in Section 5. Seem very disconnected? For instance, Line 501: ←C\leftarrow_C←C​ this has a different type to the semantics in the previous section. How does it relate? Generally, there are a lot of things that are similar to the previous section, but you are not actually connecting them. Is this because they are different or just missing exposition.

Much of the content that may seem disconnected takes the form of a
parameterizable relation and its various instantiations in different
versions of the property. \rightarrow_C is parameterized by the type ctx, which
is section 5 is instantiated as (K -> SD)x(list(target)). In later sections
it will be instantiated by other types.  Then for any \rightarrow_C, we can
extend \rightharpoonup to form \rightharpoonup_C.
[BCP: The formatting here makes it hard to read.  Can we improve it?]

We will do more to call out which parts of the formalization are
parameterized and when they are being instantiated, so that the connections
are clearer.

> Line 329: I was really interested in address taken at this point, and
  whether the model could handle it. I really think the informal aspects of
  the extensions, should be pulled forward, so these questions are answered
  earlier

@@

This is a good point, and we will examine ways to introduce that
information sooner. But we are hesitant to go into too much detail on
variants while introducing the basic formalism, because it can be a
lot for the reader to keep track of.

> Line 349: How does this related to control flow integrity/guard, and
  Intel's CET?

### 2021-09-09 submission3/response.txt

- SubroutineSimple.v defines the basic stack safety properties.
  Some comments are outdated, and will be updated or removed for the final
  submission.

  &#8594;<sub>C</sub> => Line 126 (disregard comment regarding returns)
  Definition 5.2 => Line 184
  Definition 5.9 => Line 255
  Definition 5.10 => Line 277

- CalleeSave.v defines stack safety with callee-save registers.
  &#8594;<sub>C</sub> => Line 62
  Definition 8.6 => Line 123 & Line 130
  These definitions refer to general integrity and confidentiality properties for arbitrary
  traces defined in TraceProperties.v at Lines 51 & 60.

- SubroutineShare.v defines the version enhanced with argument passing on the stack.
  Note that a preliminary treatment of address-taken locals is present; we discuss this briefly
  in the submission at line 960, but find it uninteresting in a model that lacks a heap.

@@

Conventional ISAs do not make this distinction.  Our ongoing work on the
Cerise capability machine formalization has required some
modifications to our model to distinguish values from addresses, as
they are _not_ the same in a capability machine, but it has little
global effect on the model itself. Indeed, distinguishing between
values and addresses is a higher-level abstraction that can "hide"
potential bugs resulting from implicit conversions between them, so we
feel it is preferable to model them as the same when possible.

> Another example is the outside qualifier that characterizes only a whole
> component. Wouldn't you need a finer-grain access control policy (and a
> qualifier for partially outside components)?

We don't entirely understand this question, but we wonder whether there may
be some confusion arising from our use of the term "components."  In our
model (see line 398), components are already fine-grained: individual
registers and memory addresses. We recognize that this is a poor choice of
term given the common usage of component to refer to a larger module in a
compartmentalization context, and we plan to change the term to "state
elements."  Since components/elements are so fine-grained, there is no need
for finer access control.

> Could you comment on the Coq formalization that is provided as a
>  supplementary material? Moreover, I looked at the Coq development and found some
>  admitted lemmas in it.

We have discussed the Coq formalization broadly in our general response.
The theorems and lemmas in the formalization files serve only as
sanity checks on our definitions. The Admitted and commented-out ones
are mostly part of an early effort to formalize the relationships
between our various properties, especially that Stepwise properties are stronger
than Observational ones. They were included by mistake.
_[APT: Maybe this should move up to the top-level discussion of the formalization? Not sure.]_
_[SNA: We probably wouldn't bring them up if not asked explicitly.]_

> Was it straightforward to write a Coq program from a C++ program?

_[SNA: I think this is what they meant.]_
If this question is referring to the example RISCV programs in the Coq
development, they do not necessarily correspond to C++ programs. They served as
intended as early test-cases for the property checker. More broadly, we do not
generate specifically C or C++ code for the testing, but arbitrary low-level code
that contains C-like call and return conventions.

### 2021-09-09 submission3/response.txt

> Line 329: I was really interested in address taken at this point, and
>  whether the model could handle it. I really think the informal aspects of
>  the extensions, should be pulled forward, so these questions are answered
>  earlier

This is a good point, and we will examine ways to introduce that
information sooner. But we are hesitant to go into too much detail on
variants while introducing the basic formalism, because it can be a
lot for the reader to keep track of.

> Line 349: How does this related to control flow integrity/guard, and
>  Intel's CET?

The identification of call points, as described in this paragraph, is
required for all our properties: integrity, confidentiality, and
well-bracketed control flow (WBCF). Software or hardware support for
control flow integrity (e.g. the CET shadow stack) could be used to
enforce WBCF, but not the other two properties.

### 2021-09-09 submission3/response.txt

We thank the reviewers for their comments and questions.
We first address the most important high-level points, then go back to
fill in detailed responses to all questions posed in the reviews.

@@

We use the RISCV specification to demonstrate that our properties are
testable in a realistic setting. We do not aim to exercise the entire RISCV
specification, and the validity of the model is not dependent on the absence
of (not stack-related) vulnerabilities in the RISCV implementation. That said,
the RISCV specification we use is complete for user mode integer
instructions (RV32IM).

> More generally, what are the limitations of the presented work?

We discuss limitations broadly in our top-level response.

> For example, in the model, there seems to be no distinction between
> values and addresses; is it a limitation?

@@

> Could you comment on the Coq formalization that is provided as a
>  supplementary material? Moreover, I looked at the Coq development and found some
>  admitted lemmas in it.

We have discussed the Coq formalization broadly in our general response.
The theorems and lemmas in the formalization files serve only as
sanity checks on our definitions. The Admitted and commented-out ones
are mostly part of an early effort to formalize the relationships
between our various properties, especially that Stepwise properties are stronger
than Observational ones. They were included by mistake.

> Was it straightforward to write a Coq program from a C++ program?

If this question is referring to the example RISCV programs in the Coq
development, they do not necessarily correspond to C++ programs. They served as
intended as early test-cases for the property checker. More broadly, we do not
generate specifically C or C++ code for the testing, but arbitrary low-level code
that contains C-like call and return conventions.

@@

> Other comments

> The supplementary material is not mentioned in the submission. Links
> to the Coq formalization would have been useful (e.g., for
> definition 7.4 that I did not fully understand in the submission, as
> K' is defined but not used, and so is n'').

@@

We agree, the Coq formalization should be better integrated into the
submission, as described at the head of this response. In the case of
definition 7.4, this is a typo. The K in the third bullet should be
K', and the last instance of n' should be n''.

> The first example programs (Fig. 1 to 4) are C programs. The
> programs in Fig. 5 and 6 are qualified as C++ programs, but they
> could be C programs and they are close to the first
> programs. Moreover, the C syntax for passing parameters by reference
> is surprising. I would have written f(&x)(line 934) and void f(int > *a)
> (line 944).

@@

Only Fig. 6 uses C++ features.  Although C programmers might indeed
try to simulate call-by-reference by passing a pointer as suggested
here, this is subtly different from a genuine by-reference argument in
C++, because the latter cannot be directly used in a first-class way
in the callee (without using the & operator, as e.g. at line 945).
Thus, legal access to the value of a by-reference argument is
restricted to the immediate callee (and any chain of sub-callees to
which the argument is handed down by reference), and we can capture
this access pattern in our policies.  On the other hand, pointer
arguments might escape into arbitrary sub-callees, and there is no
obvious way for policies in our style to specify when access through
these pointers should be permitted. We will improve the discussion at
line 954ff to clarify this point.

___________________________________________________________________________
# Reviewer B

> I found the paper did not connect the section well. Section 4
> presents a lot of details for a framework, which is then used in
> Section 5. Seem very disconnected? For instance, Line 501:
> ←C\leftarrow<sub>C</sub>←C​ this has a different type to the
> semantics in the previous section. How does it relate? Generally,
> there are a lot of things that are similar to the previous section,
> but you are not actually connecting them. Is this because they are
> different or just missing exposition.

@@

Much of the content that may seem disconnected takes the form of a
parameterizable relation and its various instantiations in different
versions of the property. &#8594;<sub>C</sub> is parameterized by the
type ctx, which is section 5 is instantiated as (K -> SD)x(list(target)).
In later sections it will be instantiated by other
types.  Then for any &#8594;<sub>C</sub>, we can extend &#8640; to
form &#8640;<sub>C</sub>.

We will do more to call out which parts of the formalization are
parameterized and when they are being instantiated, so that the
connections are clearer.

> Line 329: I was really interested in address taken at this point,
>  and whether the model could handle it. I really think the informal
>  aspects of the extensions, should be pulled forward, so these
>  questions are answered earlier

### 2021-09-09 submission3/response.txt

Our focus is on characterizing stack safety.  So we are particularly
concerned with limitations that prevent the model from applying to
realistic uses of the stack, as opposed to modeling other structures
such as the heap, which we intentionally say nothing about.  (Heap
safety has already been studied, in isolation, by [Azevedo et al 2018],
and we expect that their correctness condition and ours can be
combined cleanly to characterize correct protection of stack + heap.)

Features that we do not currently support:

- Address-taken locals. As we discuss at line 954, a satisfactory
  treatment of these seems to require integration with a more general
  model of memory safety that covers the heap and static globals too,
  such as the aforementioned model of Azevedo et al.

- Exceptions. We can see a way to extend the model to include them:
  we would model a "setjump" operation by inserting a
  special target in the return target stack. We would weaken
  well-bracketedness to allow reaching such a target from any
  depth. Since integrity and confidentiality are distinct from
  well-bracketedness and already permit the popping of multiple
  functions from the stack, they can simply treat the exception's
  target as another return target.

- Tail calls. To implement these, we would need to distinguish them
  from normal calls and extend &#8594;<sub>C</sub> to process them
  as a simultaneous return and call.

- Dynamic code generation. This would be challenging to
  integrate into our framework, because we rely on code annotations.
  But we can easily envision supporting limited cases in which
  the generated code never contains a call or other annotated instruction,
  or in which existing code is copied along with its annotations.

@@

- Concurrency. We can handle a limited form of coroutines, as described in
  8.3. Handling full-blown preemptive concurrency would require significant
  changes in our underlying machine model.

# Supplementary Coq Material #

We should have referenced the supplementary material from the submission, and
described its purpose.

The Coq formalization provided contains two parts: the formalization of our
properties, which was a conceptual aid in their development and may be
useful to readers' intuitions, and the testing framework, which is used to
validate our properties by showing that computable versions of them are
testable. The contents are laid out in detail at the end of our response,
with definitions mapped from the paper to the coq where relevant.
